On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-03-06 MS.tex
Add Ian suggestion (2/2)

The only effect of increased seed size in the above model is to produce a larger overall seedling. Under similar light conditions, larger seedlings are therefore predicted to have faster absolute growth rates. However, because the ratio of leaf area to total biomass decreases with plant size, larger seedlings are predicted to have lower mass-based relative growth rates during the earliest phases of growth \citep{Turnbull:2012ew}(Table \ref{tab:trade-offs}). Yet, as plants grow, we expect the effect of this initial size difference to be minimal, and the correlation between seed size and growth rate should therefore disappear. For larger plants, seed mass is not expected to have any distinct influence on growth rates (Table \ref{tab:trade-offs}).

@@

The 19 traits recorded (Fig. \ref{fig:fig1}) capture different components of plant ecological strategies. SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and Aarea are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}. Seed mass and maximum height capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}. Wood density and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}. Here wood density and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}. Finally, the leaf area ratio and leaf mass ratio are indicators of resource distribution to leaf \citep{Lambers:1992bj}.

Ultimately, data was recorded from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, Muller-landau_interspecific_2004, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.

@@

We used categorical groupings by ontogenetic ``stage'' to test our hypotheses regarding the effects of traits on growth rates. The authors of the 103 articles used in this analysis reported their plants as belonging to any of five different stages: ``seedling'', ``juvenile'', ``sapling'', ``adult'', ``mixed''. Because these categories were established according to the expertise of the authors, we were concerned about the risk of assigning plants of similar size to different categories when compiling data across multiple studies and vegetation types. This risk turned out to be small: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages were relatively compatible with thresholds we defined (Fig. \ref{fig:fig2}). In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m). There was also a clear break between saplings and adults in diameter (at 10 cm). Comparing these values to the bivariate relationships observed between variables (age, height, diameter) in the ``Biomass And Allometry Database'' \citep{Falster:2015}, demonstrated that the thresholds identified above for each stage transition also aligned relatively well with one another (Fig. \ref{fig:figA1}). Thus we adopted the above values as cut-offs for defining stage boundaries.

@@

The dataset included studies differing in the growth measurement used (relative or absolute), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate. These differences provide good criteria for assessing the quality of the data for addressing our hypotheses. We adopted a three-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across studies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the trait and growth were measured at the same stage (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait). We then compared these results with those from the subset of the dataset using relative growth rate, but with all other criteria relaxed. Finally, we compared results from both relative and absolute growth rates from the entire dataset.

@@

We tested an effect of ontogenetic stage on the relationship between growth rate and traits using a mixed-effect model. In this model, the response variable corresponds to the z-transformed coefficients of correlation calculated above, and it was assumed that studies within a stage shared a common mean effect, but that there was also random variation among studies, in addition to sampling variation \citep{Zuur:2009cfa}. Inclusion of this random effect allowed us to account for heterogeneity among studies, for example in experimental type, and vegetation type. For each trait, we performed a separate model and we established whether stage could explain additional variance in $z$ by comparing models with and without a stage effect using log-likelihood ratios \citep{Zuur:2009cfa}. If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the model without. Estimates of the effect size for each stage were considered significant if the CIs did not overlap with zero. Non-overlapping CIs across stages highlighted significant differences in effect sizes.

@@

All analyses were conducted with \texttt{R} software \citep{Ralanguageanden:2014wf} using packages \texttt{lme4} \citep{Bates-2014}. \texttt{metafor} \citep{Viechtbauer-2010}, and \texttt{gpplot2} \citep{Wickham:2009}.

@@

\subsection*{Representation of ontogenetic stages among 19 traits}
In total, correlations had been reported for at least two different stages across 17 traits out of the 19 targeted (Fig. \ref{fig:fig1}). We had thought it likely that for some traits, correlations would be reported only for one growth stage. But this limitation applied only for NARmass and vessel density, where studies appeared confined to seedling and adult stages respectively. However, for a majority of traits the number of observations across stage was highly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a same stage (Fig. \ref{fig:fig1}).

@@

For wood density, results were consistent with the prediction for negative correlations with relative growth rate across all plant sizes (Fig. \ref{fig:fig3}b). Accordingly, model fits were marginally improved when stage was incorporated (p.value = 0.049). Note that the CIs did not cross zero for seedling and sapling stage despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation and/or a good consistency in the coefficient reported for each stage across studies.

@@

As expected for seed mass, the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero). However, the correlation between seed mass and relative growth rate at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and CIs overlapping in Fig. \ref{fig:fig3}c). Again we could not distinguish between these alternatives. But unlike maximum height, the number of coefficients reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that CIs overlapping zero at adult stage were due to variation in correlation coefficients reported rather than to a much smaller numbers of replicates.

@@

We now report results for relative growth rate from the entire dataset. Our aim is to determine if additional data alters or reinforces the above conclusions, by increasing replication. This entire dataset included correlations measured with relative growth rate exclusively (Fig. \ref{fig:fig3}), across at least two species (but measured using several individuals), and did not control for the source of trait or growth (i.e. traits could be measured on a different ontogenetic stage to growth data) or environmental conditions. The relaxed criteria increased the number of replicates, from $n = 137$ to $n = 167$ correlations across 93 articles. However, the additional replicates were unequally distributed across trait-stage combinations. Some trait-stage combinations that already had a lot of data got even more support (e.g. from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates. On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: Wood density-seedling, maximum height-sapling, maximum height-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.

@@

The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass. Overall, the models fit did not improve when growth measurement was incorporated (see log likelihood ratio tests in Fig. \ref{fig:fig4}). For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g. effect size for relative and absolute growth rate of Hmax and Wood density at adult stage in Fig. \ref{fig:fig4} b and c). However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with abolute versus relative growth rate. For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero). While these results were consistent with expectations, our ability to conclude was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig. \ref{fig:fig4}d). For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.

@@

The meta-analysis reported here demonstrates that for several key traits, the influence of the trait on growth rate change as plants grow from small to large. While the possibility has been raised recently that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}, this is the first time that specific mechanistic hypotheses have been corroborated against a wide array of existing studies. Meta-analysis allowed us to generalize and thus to reach a consensus about the effect of traits on growth, even if our conclusions were at times biased toward a particular growth stage, due to uneven coverage of the empirical literature across trait-growth-stage combinations. Growth rates were already known to change with size \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd}, in other words individual plants follow a growth trajectory. Our results suggest species traits should be understood as influencing this trajectory and potentially re-ranking growth rates between individuals from different species as their size increases. This is a shift in outlook compared to much present thinking, whereby traits are seen as rendering species fast-growing or slow-growing throughout life.

@@

Increasing support costs also devalue the benefits of cheap leaf construction (low SLA), because as plant's grow larger, an increasing amount of total biomass production is devoted to building and maintaining support tissues \citep{Givnish:1995ta,King-2011}. The net result is that the growth advantage experienced by high SLA species at small sizes, dissapates among larger plants. While it has previously been noted that the correlation of SLA with growth rate disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), our meta-analysis generalises that result. Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by individuals with low SLA \citep{Reich:1992wm, Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended. Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}. In another modelling study, the SLA optimising growth rate was found to decrease with plant size, because of cross connections with the amount of self-shading in the crown and the increase in support costs in larger plants \citep{King-1999}. In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.

For wood density the meta-analysis showed negative correlation with relative growth rate across all ontogenetic stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}. It should be noted however that there are few data available to test this proposition at seedling stage (n=1-4). In our model, cheaper stem construction is responsible for the predicted negative correlation. Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.
For seedlings a negative correlation arose regardless of whether wood density was measured on adult plants, or calculated as seedling stem segment dry weight over its volume (i.e. stem density in  \citealt{CastroDiez:1998gz}), suggesting that both measurements could be used.

>>>>

The only effect of increased seed size in the above model is to produce a larger overall seedling. Under similar light conditions, larger seedlings are predicted to have faster absolute growth rates. However, because the ratio of leaf area to total biomass decreases with plant size, larger seedlings are predicted to have lower mass-based relative growth rates during the earliest phases of growth \citep{Turnbull:2012ew}(Table \ref{tab:trade-offs}). Yet, as plants grow, we expect the effect of this initial size difference to be minimal, and the correlation between seed size and growth rate should therefore disappear. For larger plants, seed mass is not expected to have any distinct influence on growth rates (Table \ref{tab:trade-offs}).

@@

The 19 traits recorded (Fig. \ref{fig:fig1}) capture different components of plant ecological strategies. SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and Aarea are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}. Seed mass and maximum height capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}. Wood density and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}. Here wood density and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}. Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf versus other tissue types \citep{Lambers:1992bj}.

Ultimately, data were recorded from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, Muller-landau_interspecific_2004, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.

@@

We used categorical groupings by ontogenetic ``stage'' to test our hypotheses regarding the effects of traits on growth rates. The authors of the 103 articles used in this analysis reported their plants as belonging to any of five different stages: ``seedling'', ``juvenile'', ``sapling'', ``adult'', ``mixed''. Because these categories were established according to the expertise of the authors, we were concerned about the risk of assigning plants of similar size to different categories when compiling data across multiple studies and vegetation types. This risk turned out to be small: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages were relatively compatible with thresholds we defined ourselves (Fig. \ref{fig:fig2}). In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m). There was also a clear break between saplings and adults in steam diameter (at 10 cm). Comparing these values to the bivariate relationships observed between variables (age, height, diameter) in the ``Biomass And Allometry Database'' \citep{Falster:2015}, demonstrated that the thresholds identified above for each stage transition also aligned relatively well with one another (Fig. \ref{fig:figA1}). Thus we adopted the above values as cut-offs for defining stage boundaries.

@@

The dataset included studies differing in the growth measurement used (relative or absolute), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate. These differences provide good criteria for assessing the quality of the data for addressing our hypotheses. We adopted a three-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across studies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the trait and growth were measured at the same stage (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait). We then compared these results with those from the subset of the dataset using relative growth rate, but with all other criteria relaxed. Finally, we compared results from both relative and absolute growth rates, from the entire dataset.

@@

We tested an effect of ontogenetic stage on the relationship between growth rate and traits using a mixed-effect model. In this model, the response variable corresponds to the z-transformed coefficients of correlation calculated above, and it was assumed that studies within a stage shared a common mean effect, but that there was also random variation among studies, in addition to sampling variation \citep{Zuur:2009cfa}. Inclusion of this random effect allowed us to account for heterogeneity among studies, for example in experimental type, and vegetation type. For each trait, we ran a separate model and established whether stage could explain additional variance in $z$ by comparing models with and without a stage effect using log-likelihood ratios \citep{Zuur:2009cfa}. If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the model without. Estimates of the effect size for each stage were considered significant if the CIs did not overlap with zero. Non-overlapping CIs across stages highlighted significant differences in effect sizes.

@@

All analyses were conducted with \texttt{R} software \citep{Ralanguageanden:2014wf} using packages \texttt{lme4} \citep{Bates-2014}, \texttt{metafor} \citep{Viechtbauer-2010}, and \texttt{gpplot2} \citep{Wickham:2009}.

@@

\subsection*{Representation of ontogenetic stages among 19 traits}
In total, correlations had been reported for at least two different stages across 17 traits out of the 19 targeted (Fig. \ref{fig:fig1}). We had thought it likely that for some traits, correlations would be reported only for one growth stage. But this limitation applied only for NARmass and vessel density, where studies appeared confined to seedling and adult stages respectively. However, for a majority of traits the number of observations across stage was highly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from the same stage (Fig. \ref{fig:fig1}).

@@

For wood density, results were consistent with the prediction for negative correlations with relative growth rate across all plant sizes (Fig. \ref{fig:fig3}b). Accordingly, model fits were marginally improved when stage was incorporated (p-value = 0.049). Note that the CIs did not cross zero for seedling and sapling stage despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation and/or a good consistency in the coefficient reported for each stage across studies.

@@

As expected, for seed mass the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero). However, the correlations between seed mass and relative growth rate at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and CIs overlapping in Fig. \ref{fig:fig3}c). Again we could not distinguish between these alternatives. But unlike maximum height, the number of coefficients reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that CIs overlapping zero at adult stage were due to variation in correlation coefficients reported rather than to a much smaller numbers of replicates.

@@

We now report results for relative growth rate from the entire dataset. Our aim here was to determine if additional data alters or reinforces the above conclusions, by increasing replication. For this analysis our dataset included correlations concerning relative growth rate exclusively (Fig. \ref{fig:fig3}), measured across at least two species (but using several individuals), and did not control for the source of trait or growth (i.e. traits could be measured on a different ontogenetic stage to growth data) or environmental conditions. The relaxed criteria increased the number of replicates, from $n = 137$ to $n = 167$ correlations across 93 articles. However, the additional replicates were unequally distributed across trait-stage combinations. Some trait-stage combinations that already had a lot of data got even more support (e.g. from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates. On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: Wood density-seedling, maximum height-sapling, maximum height-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.

@@

The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass. Overall, the model fits did not improve when information about growth measurement used (relative vs absolute growth rates) was incorporated in the model (see log likelihood ratio tests in Fig. \ref{fig:fig4}). For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g. effect size for relative and absolute growth rate of Hmax and wood density at adult stage in Fig. \ref{fig:fig4} b and c). However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with abolute versus relative growth rate. For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero). While these results were consistent with expectations, our ability to draw any firm conclusions was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig. \ref{fig:fig4} d). For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non-significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.

@@

The meta-analysis reported here demonstrates that for several key traits, the influence of the trait on growth rate changes as plants grow from small to large. While the possibility has been raised recently that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}, this is the first time that specific mechanistic hypotheses have been corroborated against a wide array of existing studies. Meta-analysis allowed us to generalize and thus to reach a consensus about the effect of traits on growth, even if our conclusions were at times biased toward a particular growth stage, due to uneven coverage of the empirical literature across trait-growth-stage combinations. Growth rates were already known to change with size \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd}, in other words individual plants follow a growth trajectory. Our results suggest species traits should be understood as influencing this trajectory and potentially re-ranking growth rates between individuals from different species as their size increases. This is a shift in outlook compared to much present thinking, whereby traits are seen as rendering species fast-growing or slow-growing throughout life.

@@

Increasing support costs also devalue the benefits of cheap leaf construction (low SLA), because as plant's grow larger, an increasing amount of total biomass production is devoted to building and maintaining support tissues \citep{Givnish:1995ta,King-2011}. The net result is that the growth advantage experienced by high SLA species at small sizes, dissipates by the time large plante size are attained. While it has previously been noted that the correlation of SLA with growth rate disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), our meta-analysis generalises that result. Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by individuals with low SLA \citep{Reich:1992wm, Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended. Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}. In another modelling study, the SLA that lead to optimal growth rate was found to decrease with plant size, because of the interplay with the degree of self-shading in the crown and the fact that support costs are greater in larger plants \citep{King-1999}. In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.

For wood density the meta-analysis showed negative correlations with relative growth rate at all ontogenetic stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}. It should be noted however that there are few data available to test this proposition at seedling stage (n=1-4). In our model, cheaper stem construction is responsible for the predicted negative correlation. Lower xylem conductance in higher density sapwood and the associated lower photosynthetic potential, has also been suggested \citep[reviewed by][]{Chave:2009iy}.
For seedlings a negative correlation arose regardless of whether wood density was inferred from measurements made on adult or measured in fact in seedlings (e.g. stem density in  \citealt{CastroDiez:1998gz}), suggesting that both measurements could be used.
